---
title       : Developing Data Products Project
subtitle    : Johns Hopkins University
author      : Tri Le
job         : Data Scientist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides  
  

---

## Application: Data Explorer

<br>

#### **Introduction**  
  

- What is this application used for?  

  *This application is used for exploratory data analysis on the ToothGrowth dataset.*

- Why do you want to choose this application?  

  *It's helpful, easy to use, and free.*


--- .class #id

## Application: Data Explorer  
  
- This application runs the following R code to generate the histogram:

```{r, fig.width=8, fig.height=4, fig.align='center'}
data(ToothGrowth)
hist(ToothGrowth$len, probability=TRUE, breaks=20, xlab='tooth length', col='lightblue', 
     main='Histogram of Tooth Length')
lines(density(ToothGrowth$len, adjust=0.5), col="red")
```         


---

## Application: Data Explorer  
  
- And the following R code to generate the regression model:

```{r, fig.width=8, fig.height=4, fig.align='center'}
with(ToothGrowth, {plot(len~dose, main="Regression Plot", xlab="dose", ylab="tooth length", 
                        col="blue")
                   abline(lm(len~dose, data=ToothGrowth), col="red") })
```         


---

## Application: Data Explorer

<br>

- This application has been developed and deployed at:  
[https://wawww.shinyapps.io/shinyapp_proj](https://wawww.shinyapps.io/shinyapp_proj)  
  
- The source code of this application can be obtained at:  
[https://github.com/wawww/shinyapp_proj](https://github.com/wawww/shinyapp_proj)


